On Secure Delegation of SampBQP with a Classical Client

### 2019-11-27 hamiltonian.tex
Rename XZ-circuit to HT-circuit

First, fix $L\in\bbN$ and define the following that implicitly depends on $L$.

\begin{definition}
	Let $\mathcal{G}_{XZ}=\set{U_0\otimes U_1\otimes\ldots\otimes U_n: U_i\in\set{I,X,Z}, \norm{\set{i: U_i\ne I}}\leq L}$
\end{definition}

@@

We define a certain form of quantum circuit that is still universal.

\begin{definition}
	Let $C$ be an XZ-circuit if $C=U_T\ldots U_1$ where $U_i\in\spn\mathcal{G}_{XZ}$.
\end{definition}

\begin{theorem}
	Given a circuit $C$ and classical input $x$, a $\BPP$ machine can reduce it to an XZ-circuit $C'$ and classical input $x'$.
\end{theorem}

We define and construct an instance of Local Hamiltonian that encodes the history of the computation.

\begin{definition}
	Let $C(x)$ be an XZ-circuit. Then let $H_{C(x)}$ be with the following properties:
	\begin{itemize}
		\item $H_{C(x)}$ can be written as $\sum_{S\in\mathcal{G}_{XZ}} d_S S$, where each $S$ has at most constantly many non-identity components.
		\item It has an eigenvector $\ket{\psi_{C(x)}}=\sum_{t=0}^TU_t\ldots U_1\ket{x}\otimes\ket{\hat{t}}$ with eigenvalue $0$.
		\item Let $\ket\phi$ be such that $\braket{\phi|\psi_{C(x)}}=0$, then $\braket{\phi|H_{C(x)}|\phi}>\frac{3}{4}$.
	\end{itemize}
\end{definition}

@@

\begin{theorem}
	Given XZ-circuit $C$ and classical $x$, a $\BPP$ machine can construct a description of $H_{C(x)}$ in polynomial time.
\end{theorem}

\begin{theorem}
	Given XZ-circuit $C$ and $x$, there exists an quantum algorithm that accepts $\ket{\psi_{C(x)}}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H|\phi}$. Furthermore, this algorithm doesn't apply any quantum gates, and uses only $X$ and $Z$ measurements.
\end{theorem}

@@

\begin{observation}
	\label{idpadding}
	Given XZ-circuit $C$ and $x$, one can first pad $C$ with identity matrices at the end, doubling its number of gates and obtain $C'$. One can then measure the last register of $\psi_{C'(x)}$ and obtain with probabiliy $\frac{1}{2}$ the state $C(x)$.
\end{observation}

\subsection{XZ-circuits}

Here we prove that XZ-circuits are universal. After this subsection, we'll be able to assume without loss of generality that all quantum circuits are XZ-circuits.

@@

We verify that our new gate set can be written as combinations of $X$ and $Z$ matrices.

@@

\begin{theorem}
	Let $C=U_T\ldots U_1$ be a XZ-circuit, and let $x\in\set{0, 1}^*$. Then a classical machine can construct in polynomial time descriptions of some $H_{C(x)}\in\spn\mathcal{G}_{XZ}$ such that:
	\begin{itemize}
		\item its ground state is $$\ket{\psi_{C(x)}}=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
		\item $\braket{\psi_{C(x)}|H_{C(x)}|\psi_{C(x)}}=0$
		\item $\forall\ket\phi,\braket{\phi|\psi_{C(x)}}=0\Rightarrow\braket{\phi|H_{C(x)}|\phi}\geq\frac{3}{4}$
		\item Has $O(T)$ nonzero components whose coefficients are each at most $O(T^3)$.
	\end{itemize}
\end{theorem}

@@

	We can also write $H=\spn\mathcal{G}_{XZ}$. Note that $U^\dagger=U$, since the gates are either Hadamard or Toffoli. Additionally, $\frac{1}{2}(I-Z_{t-1})$ annihilates time steps before $t-1$. $\frac{1}{2}(I+Z_{t+1})$ similarly annihilates steps $t+1$ and after.
	$$H_{prop,t}=\frac{I}{4}\otimes(I-Z_{t-1})(I+Z_{t+1})-\frac{U}{4}\otimes(I-Z_{t-1})X_t(I+Z_{t+1})$$
	Extra care must be taken for boundary cases.
	$$H_{prop,1}=\frac{1}{2}(I+Z_2)-U_1\otimes\frac{1}{2}(X_1+X_1Z_2)$$
	$$H_{prop,T}=\frac{1}{2}(I-Z_{t-1})-U_T\otimes\frac{1}{2}(X_T-Z_{T-1}X_T)$$

>>>>

We will first show that $\set{H, T}$ is a universal gate set.

\begin{definition}
	Call $C$ an $HT$-circuit if it consists of only Hadamard and Toffoli gates.
\end{definition}

\begin{theorem}
	Given a circuit $C$ and classical input $x$, a $\BPP$ machine can reduce it to an $HT$-circuit $C'$ and classical input $x'$.
\end{theorem}

We then define and construct an instance of Local Hamiltonian that encodes the history of the computation.
First, fix $L\in\bbN$ and define the following that implicitly depends on $L$.

\begin{definition}
	Let $\mathcal{G}_{XZ}=\set{U_0\otimes U_1\otimes\ldots\otimes U_n: U_i\in\set{I,X,Z}, \abs{\set{i: U_i\ne I}}\leq L}$
\end{definition}

@@

\begin{definition}
	Let $C(x)$ be an $HT$-circuit. Then let $H_{C(x)}$ be with the following properties:
	\begin{itemize}
		\item $H_{C(x)}$ can be written as $\sum_{S\in\mathcal{G}_{XZ}} d_S S$ with at most $O(T)$ terms
		\item Has an eigenvector $\ket{\psi_{C(x)}}=\sum_{t=0}^TU_t\ldots U_1\ket{x}\otimes\ket{\hat{t}}$ with eigenvalue $0$.
		\item Let $\ket\phi$ be such that $\braket{\phi|\psi_{C(x)}}=0$, then $\braket{\phi|H_{C(x)}|\phi}>\frac{3}{4}$.
	\end{itemize}
\end{definition}

@@

\begin{theorem}
	Given $HT$-circuit $C$ and classical $x$, a $\BPP$ machine can construct a description of $H_{C(x)}$ in polynomial time.
\end{theorem}

\begin{theorem}
	Given $HT$-circuit $C$ and $x$, there exists an quantum algorithm that accepts $\ket{\psi_{C(x)}}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(T)})\braket{\phi|H|\phi}$. Furthermore, this algorithm doesn't apply any quantum gates, and uses only $X$ and $Z$ measurements.
\end{theorem}

@@

\begin{observation}
	\label{idpadding}
	Given $HT$-circuit $C$ and $x$, one can first pad $C$ with identity matrices at the end, doubling its number of gates and obtain $C'$. One can then measure the last register of $\psi_{C'(x)}$ and obtain with probabiliy $\frac{1}{2}$ the state $C(x)$.
\end{observation}

\subsection{$HT$-circuits}

Here we prove that $HT$-circuits are universal. After this subsection, we'll be able to assume without loss of generality that all quantum circuits are $HT$-circuits.

@@

Note that our new gate set can be written as linear combinations of $X$ and $Z$ matrices.

@@

\begin{theorem}
	Let $C=U_T\ldots U_1$ be a $HT$-circuit, and let $x\in\set{0, 1}^*$. Then a classical machine can construct in polynomial time descriptions of some $H_{C(x)}\in\spn\mathcal{G}_{XZ}$ such that:
	\begin{itemize}
		\item its ground state is $$\ket{\psi_{C(x)}}=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
		\item $\braket{\psi_{C(x)}|H_{C(x)}|\psi_{C(x)}}=0$
		\item $\forall\ket\phi,\braket{\phi|\psi_{C(x)}}=0\Rightarrow\braket{\phi|H_{C(x)}|\phi}\geq\frac{3}{4}$
		\item Has $O(T)$ nonzero components whose coefficients are each at most $O(T^3)$.
	\end{itemize}
\end{theorem}

@@

	We can also write $H_{prop}\in\spn\mathcal{G}_{XZ}$. Note that $U^\dagger=U$, since the gates are either Hadamard or Toffoli. Additionally, $\frac{1}{2}(I-Z_{t-1})$ annihilates time steps before $t-1$. $\frac{1}{2}(I+Z_{t+1})$ similarly annihilates steps $t+1$ and after.
	$$H_{prop,t}=\frac{I}{4}\otimes(I-Z_{t-1})(I+Z_{t+1})-\frac{U}{4}\otimes(I-Z_{t-1})X_t(I+Z_{t+1})$$
	Extra care must be taken for boundary cases.
	$$H_{prop,1}=\frac{1}{2}(I+Z_2)-U_1\otimes\frac{1}{2}(X_1+X_1Z_2)$$
	$$H_{prop,T}=\frac{1}{2}(I-Z_{t-1})-U_T\otimes\frac{1}{2}(X_T-Z_{T-1}X_T)$$
